\documentclass[]{styling}
\usepackage{fancyhdr}

\pagestyle{fancy}
\fancyhf{}

\begin{document}

% Last Updated Date In Top Right : Comment out before finalizing.
% \lastupdated

% Header
\namesection{Jonathan Turner}{ %\urlstyle{same}\href{http://example.com}{example.com}| \href{http://example2.co}{example2.co}\\
Atlanta, GA | \href{mailto:LTurnerJonathan@gmail.com}{LTurnerJonathan@gmail.com} | \href{tel:6783783789}{678-378-3789}
}

%% Left Column

\newsavebox{\ColA}
\newsavebox{\ColB}

\sbox{\ColA}{
    \begin{minipage}[t]{0.33\textwidth}
        \vspace{0pt} 

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     EDUCATION
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        
        \section*{Education}
        \hrule
        \vspace{1 em}
        \subsection{Kennesaw State (KSU)}
        \descript{B.S. in Computer Science\newline Concentraion in Artificial Intelligence}
        \location{May 2025 | Kennesaw, GA}
        % College of Engineering \\
        \location{GPA: 3.8}
        \sectionsep
        
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     SKILLS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        
        \section*{Skills}
        \hrule
        \vspace{1 em}
        \subsection{Programming}
        \begin{tabbing}
            \emphs{4+ years} \=– \space 
            Java \textbullet{} Python \\
            \emphs{3+ years} \>– \space 
            HTML \textbullet{} VueJS  \\
            \emphs{1+ years} \>– \space 
            Matlab \textbullet{} R \textbullet{} C\#
        \end{tabbing}
        
        \sectionsep

        \subsection{Technology}
        Docker \textbullet{} Docker Compose \\
        PyTorch \textbullet{} OpenCV \textbullet{} YOLO \\
        MySQL \textbullet{} MariaDB \\
         
        \sectionsep
        \vspace{1 em}
        
        \subsection{Tools}
        Git / GitHub \textbullet{} JetBrains Suite \\
        VS Code \textbullet{} Script Automation \\
        JUnit  \textbullet{} RegEx \textbullet{} Virtualization \\
        \sectionsep
        
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     COURSEWORK
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        
        \section*{Coursework}
        \hrule
        \vspace{1 em}
        Artificial Intelligence \\
        Machine Vision \\
        Deep Learning \\
        Natural Language Processing \\
        \sectionsep
        
    
        
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     LINKS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        
        \section*{Socials}
        \hrule
        \vspace{1 em}
        \begin{tabbing}
            LinkedIn: \space \space \= \href{https://www.linkedin.com/in/lturnerjonathan}{\bf LTurnerJonathan} \\
            GitHub: \> \href{https://github.com/JonathanLTurner03}{\bf JonathanLTurner03} \\
            Portfolio: \> \href{https://www.atlantissrv.com}{\bf www.atlantissrv.com} \\
        \end{tabbing}
        \sectionsep
    \end{minipage}
}
%%%%%%%%%%%
%
%     COLUMN TWO
%
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

\sbox{\ColB}{
    \begin{minipage}[t]{0.6\textwidth}
        \vspace{0pt} 
        \section*{Experience}
        \hrule
        \vspace{1 em}
        \runsubsection{Wyzant}
        \descript{\hfill Undergraduate Computer Science Tutor }
        \location{August 2024 – Present \hfill \textit{Holly Springs, GA}}
        \vspace{.3 em}
        \vspace{\topsep} % Hacky fix for awkward extra vertical space
        \begin{tightemize}
            \item Tutor students in coursework including Machine Learning, Algorithms 
            \& Data Structures, Operating Systems, and Computer Organization \& Architecture.
            \item Manage client relationships and scheduling, maintaining a five-star profile.
        \end{tightemize}
        \sectionsep

        \runsubsection{Geek Squad}
        \descript{\hfill Consultation \& Advanced Repair Agent }
        \location{April 2021 – Present \hfill \textit{Kennesaw, GA}}
        \begin{tightemize}
            \item Diagnose and resolve technical hardware and software problems utilizing learned 
            troubleshooting techniques and specialty software.
            \item Conduct in-depth consultations with customers experiencing technological challenges, 
            actively listening to understand their needs, frustrations, and goals.
            \item Provide consistent and accurate communication and documentation to internal staff 
            and customers.
        \end{tightemize}
        \sectionsep

        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
        %     PROJECTS
        %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

        \section*{Projects}
        \hrule
        \vspace{1 em}
        \runsubsection{IcarusEye}
        \descript{\hfill Machine Vision Project}
        \location{Aug 2024 – Present \hfill Real-time Drone Object Detection}
        \begin{tightemize}
            \item Develop IcarusEye, a real-time object detection and tracking application that leverages 
            a custom YOLOv8s model trained on the Visdrone2019-DET dataset and integrates ByteTrack for 
            robust performance.
            \item Implement dynamic features including live control of confidence thresholds, model swapping, 
            class omission, and FPS adjustments, enhancing customization and real-time responsiveness.
            \item Optimize the application for edge device deployment, ensuring efficient resource management 
            and reliable performance in varied operational environments regardless of drone capabilities.
        \end{tightemize}
        \sectionsep

        \runsubsection{GSO Website Unification}
        \descript{\hfill Capstone Project}
        \location{Jan 2025 – May 2025 \hfill Lead Designer \& Developer}
        \begin{tightemize}
            \item Collaborated with a team to develop a proof-of-concept website consolidation project for the 
            Georgia Symphony Orchestra, unifying multiple domains into a single, cohesive platform.
            \item Designed and implemented custom WordPress themes, plugins, and API hooks to integrate the 
            ticketing system more effectively and enhance overall site functionality.
            \item Leveraged modern web design practices and responsive development techniques to ensure an 
            optimal user experience and consistent brand identity.
        \end{tightemize}
        \sectionsep
    \end{minipage}
}

\noindent\usebox{\ColA}\hfill\usebox{\ColB}

\end{document}  \documentclass[]{article}