\section{Field Implementation Engineer}

I am excited to apply for the Field Engineer 
position at ST Engineering Aethon, Inc. With a Bachelor’s degree 
in Computer Science specializing in Artificial Intelligence from 
Kennesaw State University and hands-on experience developing 
innovative technical solutions, I am eager to bring my skills and 
passion to your pioneering team in robotics and automation. \par

My extensive technical background includes proficiency in Linux/Unix systems, 
networking technologies (TCP/IP, VPN, Ethernet), and practical experience 
troubleshooting both hardware and software issues. As a Consultation \& 
Advanced Repair Agent at Geek Squad, I've consistently demonstrated strong 
problem-solving abilities, diagnosing complex technical issues efficiently 
while providing excellent customer service and clear communication to clients. \par

My recent projects reflect my strong aptitude for robotics and AI applications. 
Through my development of "IcarusEye," a real-time drone-based object detection 
and tracking system integrating OpenCV, YOLO, and PyTorch, I gained valuable insights 
into deploying AI solutions in varied and dynamic environments—skills directly aligned 
with the installation, support, and optimization responsibilities outlined for this role. \par

Additionally, my experience as a Computer Science Tutor has honed my ability to 
clearly communicate complex technical concepts, aligning with your requirement for 
providing client training and ensuring customer satisfaction. 
Joining ST Engineering Aethon, Inc. represents an exciting opportunity to leverage my 
technical expertise, adaptability, and passion for robotics to support your clients 
effectively and contribute to your innovative team. \par

\softtext{Thank you very much for your consideration. I look forward to the possibility of discussing how my skills and experiences align with your goals.}